Parsing Postfix log files

### 2007-07-05 doc/logparser.tex
Parse postfix/bounce messages.  Might need some bugs shaken out of it. Change the time period for discarding cleanup lines to seven minutes because evidence from the logs shows it needs to be that high. Log the number of entries in each data source when dumping state; change the Makefile to reflect that. Save the date in results, to make debugging easier. Refactored my_warn() and my_die() to use format_error(); added a backtrace to messages too. Updated Parser documentation appropriately. Updated the paper appropriately. Expanded the mail coverage section with a breakdown of the remaining stat

@@

@@

    \item The timestamp of the cleanup line must be within six minutes of
        the mail acceptance timestamp.  Timeouts happen after five minutes,
        so six minutes gives one minute of leeway.

@@

@@

The
state table contains entries for mails not yet delivered at the end of the

>>>>

    \item [BOUNCE] Postfix 2.3 (and hopefully subsequent versions) log the
        creation of bounce messages.  This action creates a new mail if
        necessary, marking it as a bounce notification and removing the
        unknown origin flag if it exists.

@@

Postfix 2.3 (and hopefully subsequent version) log the creation of a bounce
message.

@@

    \item The timestamp of the cleanup line must be within seven minutes of
        the mail acceptance timestamp.  Timeouts happen after five minutes,
        but some data may have been transferred slowly, and empirical
        evidence suggests seven minutes is a good compromise between false
        positives and false negatives.

@@

XXX REDO THIS

@@

The state table contains entries for mails not yet delivered when the
parser finishes execution.  Ideally all it should contain are mails which
are awaiting delivery after the period covered by the logs, though it may
also contain mails from the start of the logs whose initial entries are not
contained in the logs.  Any other entries are evidence of a failure in
parsing or an aberration in the logs.  After parsing the 93 test log files
the state table contains XXX entries, breaking down into:

    \item 1 connection which started only seconds before the logs ended and
        had not completed.

    \item 9 mails which had yet to be delivered due to repeated failures.

    \item 4 mails resulting from the out of order log entries described
        above.

    \item 9 mails whose initial log entries are not present in the logs.
